Rigidity of Expectation: Additional Evidence from Density Forecasts of Professionals and Households

### 2019-06-29 paper/Draft.tex
Finished literature. Introduction has only preview of the results left before. Summary of the Theories left.

	\begin{abstract}
		Surveys on density forecasts of macroeconomic variable that are not available until recent two decades provides one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation. This paper first documents the persistent dispersion in uncertainty about future inflation across economists and households. Second,  utilizing the panel data of individual uncertainty, I provide additional test results and estimates that are not consistent with the benchmark prediction of full-information rational expectation (FIRE). Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theories of expectation rigidity and points to evidence for shock-dependent nature of the rigidity.  This sets the stage for estimating shock-specific rigidity using uncertainty as the next step of analysis.

@@

>>>>

	\begin{abstract}
		Surveys on density forecasts of macroeconomic variable that are not available until recent provides one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation. This paper first documents the persistent dispersion in uncertainty about future inflation across economists and households. Second,  utilizing the panel data of individual uncertainty, I provide additional test results and estimates that are not consistent with the benchmark prediction of full-information rational expectation (FIRE). Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theories of expectation rigidity and additional evidence for shock-dependent nature of the rigidity.  This sets the stage for estimating shock-specific rigidity using uncertainty as the next step of analysis.

@@

	This paper is related to three strands of literature. First, recent decade has seen an emergence of the empirical work directly testing and evaluating the various theories on expectations theories using survey data. For instance, \citet{mankiw2003disagreement}, \citet{carroll2003macroeconomic}, \citet{branch2004theory}. More recent examples include \citet{coibion2018firms} on firms' managers. In terms of the methodology, this paper is closest to \citet{coibion2012can} and \citet{fuhrer2018intrinsic}, In addition to testing particular sets of theories, there is also a number of papers that show people's expectations are driven by idiosyncratic demografics and macroeconomic experiences they have had. For instance, \citet{malmendier2015learning}. However, all of these research simply rely upon point forecsts instead of densitity forecast or surveyed uncertainty. This is one theme on which that this paper differs from the existing literature.

	Second, the literature that has been originally developed under the theme of forecast efficiency provides a framework analyzing the dynamics of uncertainty useful for the purpose of this paper. The focus of the forecasting efficiency literature is evaluating forecasters' performance and improving forecasting methodology, but it can be adapted into testing the context of understanding expectation formation of different types of agents. This is especially relevant to this paper as I focus on the uncertainty.

	Third, \citet{manski2004measuring} and many other papers have advocated long for elicitating probiblistic questions measuring subjective uncertainty in economic surveys. Although the initial suspicion concerning to people's ability in understanding, using and answering probabilistic questions is understandable, \citet{xx}, \citet{xx} have all shown that this is actually less of a concern. \citet{armantier2017overview} have a thorough discussion on designing, experimenting and implementing the consumer expectation surveys to insure the quality of the responses. Broadly speaking, the advocators have argued that going beyond revealed preference approach, availability to survey data provides economists with direct information on agents' expectations and helps avoids imposing arbitrary assumption.  This insight holds for not only point forecast, but also and even more importantly, for uncertainty.

	The paper is organized as followed. Section \label{theory} first sets up a common framework in which testable various theories can be compared. Also, I derive the testable predictions from these theories for individual and population uncertainty as well as other moments. Section \ref{empirical} discusses the survey data used for this paper, and presents both the stylized patterns and time series regressions that test the implications of these theories.   Section \ref{ShockBased} includes results from estimating the impulse response of forecast moments to externally identified shocks.  Section \ref{Conclusion} concludes the paper and discusses the plan for the next step.
